SIR Model With Testing Flows and Isolation

### 2020-10-22 codes/ali_test_sir.Rmd
testing function is updated, code is updated not the text

```{r, model formulation}
sir.model <- function(time,state,params){
    unpack(as.list(c(state,params)))
    ## Force of Infection  
    Lambda <- beta * (I_u + eta_w*(I_n+I_p) + eta_t*I_t)/N0
    ## scaling the weights
    sc <- t*N0/(W_s*S_u+W_i*I_u+W_r*R_u)
    # sc <- t*N0
    F_s <- sc*W_s
    F_i <- sc*W_i
    F_r <- sc*W_r

@@

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=1,gamma=1/3, omega=0.25, t=0.01, 
             W_s=0.01, W_i=1, W_r=0.01, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# Disease free equilibrium
Sn_dfe <-function(params){
  unpack(as.list(params))
  return((t*(1-P_s)*N0)/omega)
}
Su_dfe<- params[["N0"]]-Sn_dfe(params)

state_dfe <- c(S_u=Su_dfe, S_n=Sn_dfe(params),
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)

d <- seq(0,200,by=0.1)
# Conditional stop for desolver
rootfun <- function (time, state,params) { 
  unpack(as.list(c(state,params)))
  return(I_u - 1) }
```

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}
F_i <- function(state,params){
   unpack(as.list(c(state,params)))
   return(t*N0*W_i/(W_s*S_u+W_i*I_u+W_r*R_u))
 }
 # just a test
  F_i(state=state_dfe,params=update(params,t=0))

R0<-function(params){
    unpack(as.list(params))
    Sn_dfe<- Sn_dfe(params)
    Su_dfe<- N0-Sn_dfe
    F_i <-t*N0*W_i/(W_s*Su_dfe) #at DFE
    # F_i <-t*N0*W_i
    A <-gamma*(omega+gamma+eta_w*F_i) + omega*eta_t*P_i*F_i
    B <-(omega+eta_w*(F_i+gamma))*gamma+(eta_w*gamma+eta_t*omega)*(omega*P_i*F_i)/(omega+gamma)

@@

# R0 expression with eta_w/eta_t factored
R02<-function(params){
    unpack(as.list(params))
    Sn_dfe<- Sn_dfe(params)
    Su_dfe<- N0-Sn_dfe
    F_i <-t*N0*W_i/(W_s*Su_dfe) #at DFE

@@

 df1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,t=t,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=eta_w,eta_t=eta_t,s=params[["s"]])

@@

 df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,t=t,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=params[["eta_w"]],eta_t=eta_t,s=s)

>>>>

```{r, model formulation}
sir.model <- function(time,state,params){
    unpack(as.list(c(state,params)))
    ## Force of Infection  
    Lambda <- beta * (I_u + eta_w*(I_n+I_p) + eta_t*I_t)/N0
    ## scaling the weights
    sc <- tau*t*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+t*N0)
    F_s <- sc*W_s
    F_i <- sc*W_i
    F_r <- sc*W_r

@@

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=0.8,gamma=1/3, omega=0.25, t=0.01, 
             W_s=0.01, W_i=1, W_r=0.01, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2, #eta_w/eta_t
            tau=1
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
rootfun <- function (time, state,params) { 
  unpack(as.list(c(state,params)))
  return(I_u - 1) }
```

```{r DFE, message=FALSE}
# DFE; numerical approach
library(rootSolve)
DFE <- function(S,params){
  S_u <- S[1]
  S_n <- S[2]
  I_u <-0
  R_u<-0
  unpack(as.list(params))
  sc <- tau*t*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+t*N0)
  F_s <- sc*W_s

 return(c(eq1=S_u+S_n-N0,
   eq2=-F_s*S_u+omega*S_n))
}

roots_dfe <- multiroot(DFE, c(1, 1), parms = params, positive = T)
roots_dfe$root

all.equal(sum(roots_dfe$root),params[["N0"]])

# DFE; analytic approach
Su_dfe <-function(params){
  unpack(as.list(params))
  a <- t
  b <- -t+(1-t/omega)*tau*W_s
  c <- -tau*W_s
  d <- b^2-4*a*c

  return(N0*2*a/(-b+sqrt(d)))
}

Sn_dfe<- params[["N0"]]-Su_dfe(params)

state_dfe <- c(S_u=Su_dfe(params), S_n=Sn_dfe,
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)

all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}
F_i <- function(state,params){
   unpack(as.list(c(state,params)))
  sc <- tau*t*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+t*N0)
   return(sc*W_i)
 }
 # just a test
  F_i(state=state_dfe,params=update(params,t=0))

R0<-function(params){
    unpack(as.list(params))
    Su_dfe<- Su_dfe(params)
    Sn_dfe<- N0-Su_dfe
    F_i <- tau*t*N0*W_i/(tau*(W_s*Su_dfe)+t*N0) #at DFE

    A <-gamma*(omega+gamma+eta_w*F_i) + omega*eta_t*P_i*F_i
    B <-(omega+eta_w*(F_i+gamma))*gamma+(eta_w*gamma+eta_t*omega)*(omega*P_i*F_i)/(omega+gamma)

@@

# R0 expression with eta_w/eta_t factored
R02<-function(params){
    unpack(as.list(params))
    Su_dfe<- Su_dfe(params)
    Sn_dfe<- N0-Su_dfe
    F_i <-tau*t*N0*W_i/(tau*(W_s*Su_dfe)+t*N0) #at DFE

@@

 df1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,t=t,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=eta_w,eta_t=eta_t,s=params[["s"]],tau=params[["tau"]])

@@

 df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,t=t,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=params[["eta_w"]],eta_t=eta_t,s=s,tau=params[["tau"]])
